TEMPERATURES AND METALLICITIES OF M DWARFS IN THE APOGEE SURVEY

### 2019-08-01 paper/draft.tex
empirical relations

\color{gcolor}{A number of studies focused on improving M dwarf metallicity precisions have used systems of M dwarfs in common proper motion with an FGK star and strong, isolated lines in the spectra of the M dwarf (e.g. \citealt{Terrien:2012}, \citealt{Rojas-Ayala:2012}, \citealt{Newton:2014}) to developed precise empirical relations (as good as $\sim$0.07\,dex). However these metallicity calibrations are inaccessible for analysis with APOGEE, as the wavelength coverage does not include important calibration indices in the $K$-band nor information about the overall spectral shape often used to determine $\teff$ and spectral type. Further, earlier calibrations are generally based on moderate-resolution data \citep[with some exceptions,][]{Neves:2014, Lindgren:2016} that fail to utilize the greater spectral information provided by APOGEE's resolution.}\color{black}

>>>>

A number of studies focused on improving M dwarf metallicity precisions have used systems of M dwarfs in common proper motion with an FGK star and strong, isolated lines in the spectra of the M dwarf \citep[e.g.][]{Terrien:2012,RojasAyala:2010,Newton:2014,Neves:2014,Lindgren:2016} to developed precise empirical relations (as good as $\sim$0.07\,dex). 
However these metallicity calibrations do not take advantage of the full wavelength coverage, nor information about the overall spectral shape often used to determine $\teff$ and spectral type. Further, earlier calibrations are generally based on moderate-resolution data \citep[with some exceptions,][]{Neves:2014, Lindgren:2016} that fail to utilize the greater spectral information provided by APOGEE's resolution.
